### 2016-07-07 lineups.Rnw
fix dplyr issue and calculate significance of beta3s

Figure~\ref{fig:comparison} shows an overview of model estimates for each simulated data set. What we expect to see is that estimates do not change values (much) if they are estimated under a model different from the one they are generated from. This is true for all data sets estimated under model $M_1$ independently of which model they were generated from (top row of Figure~\ref{fig:comparison}). For data fitted under model $M_2$ we see that parameter $\beta_3$ (jumping transitive triplets) are estimated to be about zero, if the data is generated from models $M_1$ and $M_3$.
For model $M_2$, parameter $\beta_3$ is estimated to be significantly different from zero in almost all cases \hh{(XXX how many exactly? XXX)}. This coincides with our expectation.

@@

lus_summary_2 <- lus_spread %>% dplyr::group_by(part, lineupid, param_name) %>%
  dplyr::summarize(
    data_n = sum(true_model=="M2"),
    data_est = mean(M2[true_model=="M2"]),
    data_sd = sd(M2[true_model=="M2"], na.rm=TRUE),
    null_est = list(M2[true_model=="M1"]),
    data_dist = data_est - max(unlist(null_est))),
  upper_qu = sum(data_est > unlist(null_est)) / (n()-1) )

# XXX The lines commented out above crash my RStudio. I haven't figured out why yet! :( XXX

>>>>

<<est>>=
#For model $M_2$, parameter $\beta_3$ is estimated to be significantly different from zero in almost all cases \hh{(XXX how many exactly? XXX)}.

# get beta3s where true model and fit model are M2
beta3sig <- lus_ests_truth %>% 
  filter(true_model == "M2", model == "M2", 
         param_name == "transitive triplets jumping alcohol2")
convergebeta3 <- length(which(beta3sig$convergence == "Converged")) / nrow(beta3sig)

# get ones that converged.
beta3sig2 <- beta3sig %>% 
  filter(convergence == "Converged") %>%
  mutate(tstat = param_est/param_est_se,
         ttestpval = 2*dt(tstat, df = 1))
beta3sig05 <- sum(beta3sig2$ttestpval <= 0.05) / nrow(beta3sig2)
beta3sig10 <- sum(beta3sig2$ttestpval <= 0.10) / nrow(beta3sig2)
@
Figure~\ref{fig:comparison} shows an overview of model estimates for each simulated data set. What we expect to see is that estimates do not change values (much) if they are estimated under a model different from the one they are generated from. This is true for all data sets estimated under model $M_1$ independently of which model they were generated from (top row of Figure~\ref{fig:comparison}). For data fitted under model $M_2$ we see that parameter $\beta_3$ (jumping transitive triplets) are estimated to be about zero, if the data is generated from models $M_1$ and $M_3$.
For model $M_2$, parameter $\beta_3$ is estimated to be significantly different from zero in \st{\Sexpr{round(100 * beta3sig10, 1)}\% of cases}. This coincides with our expectation.

@@

lus_summary_2 <- lus_spread %>% dplyr::group_by(part, lineupid, param_name) %>%
  dplyr::summarize(
    data_n = sum(true_model=="M2"),
    data_est = mean(M2[true_model=="M2"]),
    data_sd = sd(M2[true_model=="M2"], na.rm=TRUE),
    null_est = list(M2[true_model=="M1"]),
    data_dist = data_est - max(unlist(null_est)),
    upper_qu = sum(data_est > unlist(null_est)) / (n()-1) 
  )

# XXX okay, i updated dplyr and it works just fine. ugh. sorry for wasting time.
